Higher-Order unification for free!

### 2024-05-13 paper/appendix.tex
fv -> ov & hv -> mv

  type decompl-subst map -> map -> ho.subst -> 
    fo.fsubst -> fo.fsubst -> o.
  decompl-subst _ [A|_] _ _ _ :- fail.
  decompl-subst _ [] _ F F.
  decompl-subst Map [mapping (fv VO) (hv VM _)|Tl] H F F2 :- 
    mem.set? VM H T, !, 
    ho.deref-assmt H T TTT,
    abs->lam TTT T', tm->to Map T' T1, 
    fo.eta-contract T1 T2, mem.assign VO F T2 F1,
    decompl-subst Map Tl H F1 F2. 
  decompl-subst Map [mapping _ (hv VM _)|Tl] H F F2 :- 
    mem.unset? VM H, decompl-subst Map Tl H F F2.

  type tm->to map -> ho.tm -> fo.to -> o.
  tm->to _ (ho.con C)  (fo.o-con C).
  tm->to L (ho.lam B1) (fo.o-lam B2) :- 
    pi x y\ tm->to _ x y => tm->to L (B1 x) (B2 y).
  tm->to L (ho.app L1) T :- map (tm->to L) L1 [Hd|Tl], 
    fo.mk-app Hd Tl T.
  tm->to L (ho.uva VM TL) T :- mem L (mapping (fv VO) (hv VM _)), 
    map (tm->to L) TL T1, fo.mk-app (fo.o-uva VO) T1 T.

@@

  type add-new-map ho.subst -> ho.tm -> map -> 
      map ->  fo.fsubst -> fo.fsubst -> o.
  add-new-map _ (ho.uva N _) Map [] F1 F1 :- 
    mem Map (mapping _ (hv N _)), !.
  add-new-map H (ho.uva N L) Map [Map1 | MapL] F1 F3 :-
    mem.new F1 M F2,
    len L Arity, Map1 = mapping (fv M) (hv N (arity Arity)),
    add-new-map H (ho.app L) [Map1 | Map] MapL F2 F3.
  add-new-map H (ho.lam B) Map NewMap F1 F2 :- 
    pi x\ add-new-map H (B x) Map NewMap F1 F2.
  add-new-map H (ho.app L) Map NewMap F1 F3 :- 
    add-new-map-aux H L Map NewMap F1 F3.
  add-new-map _ (ho.con _) _ [] F F :- !.
  add-new-map _ N _ [] F F :- name N.

>>>>

  type decompl-subst map -> map -> ho.subst -> 
    fo.fsubst -> fo.fsubst -> o.
  decompl-subst _ [A|_] _ _ _ :- fail.
  decompl-subst _ [] _ F F.
  decompl-subst Map [mapping (ov VO) (mv VM _)|Tl] H F F2 :- 
    mem.set? VM H T, !, 
    ho.deref-assmt H T TTT,
    abs->lam TTT T', tm->to Map T' T1, 
    fo.eta-contract T1 T2, mem.assign VO F T2 F1,
    decompl-subst Map Tl H F1 F2. 
  decompl-subst Map [mapping _ (mv VM _)|Tl] H F F2 :- 
    mem.unset? VM H, decompl-subst Map Tl H F F2.

  type tm->to map -> ho.tm -> fo.to -> o.
  tm->to _ (ho.con C)  (fo.o-con C).
  tm->to L (ho.lam B1) (fo.o-lam B2) :- 
    pi x y\ tm->to _ x y => tm->to L (B1 x) (B2 y).
  tm->to L (ho.app L1) T :- map (tm->to L) L1 [Hd|Tl], 
    fo.mk-app Hd Tl T.
  tm->to L (ho.uva VM TL) T :- mem L (mapping (ov VO) (mv VM _)), 
    map (tm->to L) TL T1, fo.mk-app (fo.o-uva VO) T1 T.

@@

  type add-new-map ho.subst -> ho.tm -> map -> 
      map ->  fo.fsubst -> fo.fsubst -> o.
  add-new-map _ (ho.uva N _) Map [] F1 F1 :- 
    mem Map (mapping _ (mv N _)), !.
  add-new-map H (ho.uva N L) Map [Map1 | MapL] F1 F3 :-
    mem.new F1 M F2,
    len L Arity, Map1 = mapping (ov M) (mv N (arity Arity)),
    add-new-map H (ho.app L) [Map1 | Map] MapL F2 F3.
  add-new-map H (ho.lam B) Map NewMap F1 F2 :- 
    pi x\ add-new-map H (B x) Map NewMap F1 F2.
  add-new-map H (ho.app L) Map NewMap F1 F3 :- 
    add-new-map-aux H L Map NewMap F1 F3.
  add-new-map _ (ho.con _) _ [] F F :- !.
  add-new-map _ N _ [] F F :- name N.
